---
title: "Basic Inferential Data Analysis"
author: "Khoa Tran"
date: "04/08/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview

In the second part, we are going to explore the ToothGrowth dataset and use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

## Part 2

Load the needed library
```{r}
library(ggplot2)
```

In this second part, we will work with the ToothGrowth dataset
```{r}
str(ToothGrowth)

ggplot(ToothGrowth, aes(dose,len)) + geom_point(aes(col = supp))
```

As the can see, there seem to be differences between 2 type of supplementary at different dose level. We will perform hypothesis tests to confirm this.


```{r}
OJ <- subset(ToothGrowth, supp == "OJ")
VC <- subset(ToothGrowth, supp == "VC")

```

#### OJ vs VC at the 0.5 dose level

```{r}
OJ_0.5 <- subset(OJ, dose == 0.5)
VC_0.5 <- subset(VC,dose == 0.5)
```

First we let check the len firgure has the same variance or not
```{r}
sd(OJ_0.5$len)^2 / sd(VC_0.5$len)^2
```
As this is about 2.6 we can asume that they do not have the same variance

Perform the t-test
```{r}
t.test(OJ_0.5$len,VC_0.5$len,paired = FALSE, var.equal = FALSE ,alternative = "greater")
```
As the p-values is 0.003179 is lower that our significant level 0.05 . Therefore , we can reject the null hypothesis. And it is very likely that OJ at this dose level is more effective that VC

#### OJ vs VC at the 1 dose level

```{r}
OJ_1 <- subset(OJ, dose == 1)
VC_1 <- subset(VC,dose == 1)
```

First we let check the len firgure has the same variance or not
```{r}
sd(OJ_1$len)^2 / sd(VC_1$len)^2
```
As this is about 2.4 we can asume that they do not have the same variance

Perform the t-test
```{r}
t.test(OJ_1$len,VC_1$len,paired = FALSE, var.equal = FALSE, alternative = "greater")
```
As the p-values is 0.0005192 is lower that our significant level 0.05 . Therefore , we can reject the null hypothesis. And it is very likely that OJ at this dose level is more effective that VC

#### OJ vs VC at the 2 dose level

```{r}
OJ_2 <- subset(OJ, dose == 2)
VC_2 <- subset(VC,dose == 2)
```

First we let check the len firgure has the same variance or not
```{r}
sd(OJ_2$len)^2 / sd(VC_2$len)^2
```
As this is about 0.3062501 we can asume that the tooth growth rate is this level have same variance

Perform the t-test
```{r}
t.test(OJ_2$len,VC_2$len,paired = FALSE, var.equal = TRUE, alternative = "greater")
```
As the p-values is 0.5181 is larger that our significant level 0.05 . Therefore , we are fail to reject the null hypothesis. 

### Conclusion
In the first 2 dose level, 0.5 and 1, there are a reasonable evidence to state that the OJ help to growth better than VC. However, at the 2 dose level, there are not enough evidence to conclude the samething, and we have to assume there are no difference between them.

### Assumptions
- The data is collect randomly without any bias
- The data is independence with the sample size < 10% of the population
- The parent population is normally distributed
